\documentclass[a4paper,12pt]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{purple}            

\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}  

\name{Gilbert}{Kipkech}
\title{Resume}
\address{Nairobi, Kenya}{}{}       
\phone[mobile]{0702184141 / 0738641360}   
\email{gilbertkipkech1995@gmail.com}

\begin{document}

\maketitle
\section{Profile Summary}
\cvitem{}{
I am a certified Information Technology professional with a background in computer security, networking, project management, digital networks, Huawei switch and routing, software installation, and hardware maintenance. I am detail-oriented and a problem-solver who excels at providing optimal solutions, considering all aspects and consequences. I am friendly, professional, and build strong rapport with both team members and clients. I am seeking a hands-on position that allows me to apply my skills and experience to contribute to the organization while advancing my career.}

\section{Education}
\cvitem{2015 -- Ongoing}{Masters of Computer Application , Dibrugarh University, India}
\cvitem{2015 -- 2018}{BSc. Business Information Systems, Jaramogi Oginga Odinga University of Science and Technology, Kenya}
\cvitem{2011 -- 2012}{Kenya Certificate of Secondary Education (KCSE), Moi High School - Kabartonjo}
\cvitem{Date}{Kenya Certificate of Primary Education (KCPE), Sesoi Primary School}

\section{Trainings and Workshops Attended}
\cvitem{August 2019}{Basic Digital Skills Training, eMobilis Mobile Technology Institute, Nairobi}
\cvitem{July 2019}{HCIA-Routing \& Switching Training, Kenyatta University, Nairobi}

\section{Work History}
\subsection{Liquid Telecom (March 2020 - 2024)}
\textbf{Managed Help Desk Officer}
\cvitem{Duties and Responsibilities}{
\begin{itemize}
    \item Attend to system-generated tickets for platinum customers and provide 1st level checks prior to escalating to the technical service management team.
    \item Manage the ticket flow to ensure all tickets are handled on time and meet initial response SLA.
    \item Perform timely follow-ups with the internal team for fault resolution updates and populate them on the customer tickets.
    \item Ensure the effectiveness and accuracy of data sources and data gathering techniques for quality checks.
    \item Perform call-backs to assess customer satisfaction levels for all platinum customers.
    \item Generate reports for operational and analytical dashboards for decision-making.
    \item Extract and analyze data from company and external databases to optimize product development and business strategies.
\end{itemize}}

\subsection{ICT Authority (July 2019 - February 2020)}
\textbf{Presidential Digital Talent Program (Export Processing Zones Authority)}
\cvitem{Duties and Responsibilities}{
\begin{itemize}
    \item Maintain an asset register for all ICT assets at the stations.
    \item Assist in generating reports for management decision-making.
    \item Support in implementing company-wide data strategies.
    \item Conduct technical and electrical safety checks on computer equipment.
    \item Help staff and clients with technical issues and software setups.
\end{itemize}}

\subsection{Kenya National Examination Council (December 2019)}
\textbf{Data Capturer}
\cvitem{Duties and Responsibilities}{
\begin{itemize}
    \item Prepare source data for computer entry by compiling and sorting information.
    \item Review data for deficiencies and resolve them following standard procedures.
    \item Enter customer and account data by inputting information on a keyboard or optical scanner.
    \item Verify entered data by reviewing, correcting, or reentering it.
    \item Maintain confidentiality in data protection operations.
\end{itemize}}

\subsection{IEBC (May - June 2019)}
\textbf{Data Capturer}
\cvitem{Duties and Responsibilities}{
\begin{itemize}
    \item Verify and cross-check data captured for voter registration.
    \item Confirm names, IDs, and other details in the soft copy are accurate from hard copies submitted by the promoters.
    \item Submit verification reports to the supervisor.
\end{itemize}}

\subsection{Kenya Literature Bureau (March 2017 - July 2017)}
\textbf{Industrial Attaché (Information Systems Analyst)}
\cvitem{Duties and Responsibilities}{
\begin{itemize}
    \item Responsible for ERP configuration and fiber optic cable termination.
    \item Provided ICT support, handled Sage ACCPAC ERP, and web design.
    \item Troubleshot computer-related issues and ensured correction of data updates in the system.
\end{itemize}}

\section{Professional Memberships}
\cvitem{HCIA Routing \& Switching}{Huawei Certified Information Associate (Routing and Switching).}
\cvitem{Internet Society}{Member of the Internet Society.}

\section{Skills and Competencies}
\cvitem{Software}{Microsoft Office Suite (Word, Publisher, PowerPoint, Excel)}
\cvitem{Programming}{C, C++, Java}
\cvitem{Web Development}{HTML, CSS, PHP}
\cvitem{Networking}{Huawei Certified Information Associate (Routing and Switching)}

\section{Interests, Personal Attributes, and Hobbies}
\cvitem{}{In my free time, I enjoy listening to webinars on technological trends to stay current, reading motivational books, and networking.}
\cvitem{}{I have a strong ability to learn and master new technologies quickly.}
\cvitem{}{Excellent networking skills and communication abilities, enabling me to express technical concepts effectively both verbally and in writing.}

\section*{Referees}

\begin{enumerate}
    \item \textbf{Mr. Jacob Rajula} \\
    Principal ICT Technician \\
    Export Processing Zones Authority \\
    P.O. Box 50563-00200, Nairobi \\
    Tel: +254(0)456621, 6621106 \\
    Mobile: +254 721 378198 \\
    Email: \texttt{jacob.rajula@epzakenya.com}
    
    \vspace{10pt} 
    
    \item \textbf{Ms. Judy Cheruiyot} \\
    Sub-County Registrar \\
    National Registration Bureau - Baringo \\
    P.O. Box 34-30400, Kabarnet \\
    Mobile: 0727759130
    
    \vspace{10pt}
    
    \item \textbf{Ms. Ann Gachau} \\
    Retail Services \& Contact Center \\
    Liquid Interligent Technologies \\
    Sameer Business Park, Block A, Mombasa Road, Nairobi \\
    Mobile: 0734003919 \\
    Email: \texttt{ann.gachau@liquidtelecom.com}
\end{enumerate}

\end{document}